CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review to improve reproducibility

### 2021-02-23 codecheck-paper.tex
another round of edits completed.

\textbf{Step 1:} The author submits their manuscript along with the
code and data to the PUBLISHER.  The code and data need not be openly
available at this point.  However, in many cases the code and data may
be published on a code hosting platform, such as GitHub or
GitLab. Ideally, the AUTHOR is expecting the CODECHECK and prepares
for it, e.g.,~by asking a colleague to attempt a reproduction, and
providing a set of instructions on how to re-run the workflow.

\textbf{Step 2:} The publisher finds a CODECHECKER to check the
code. This is analogous to the publisher finding one or more
peer-reviewers to evaluate the paper, except we suggest that the
CODECHECKER and the author talk directly to each other.

\textbf{Step 3:} The CODECHECKER runs the code, based on instructions provided by
the author. They check if some or all of the results from the paper can be
reproduced. If there are
any problems running the code, the CODECHECKER asks the AUTHOR for help,
updates, or further documentation.
The burden to provide reproducible material lies with the author.
The CODECHECKER then tries to run the code again.
This process iterates until either the CODECHECKER is successful,
or the CODECHECKER concludes the workflow is not reproducible.
As part of this process, the CODECHECKER could work entirely locally, relying on their own computing resources, or in the cloud, e.g.,~using the open MyBinder infrastructure \cite{jupyter_binder_2018} or alternatives, some of which are more tailored to scientific publications while others offer commercial options for, e.g.,~publishers (cf. \cite{konkol_publishing_2020}).
A cloud-based infrastructure allows for the CODECHECKER and author to collaboratively improve the code and enforces a complete definition of the computing environment; but, unless secure infrastructure is provided, e.g.,~by the PUBLISHER, this requires the code and data to be published openly online.
Note that the task of the CODECHECKER is to check the ``mechanics'' of the workflow not to evaluate its correctness. 
In the context of mathematics, Stodden et~al. \cite{stodden_setting_2013} distinguish between \emph{verification} and \emph{validation};
following their definition, a CODECHECK ensures verification
%\footnote{Note this is a different use from that referred to as the \emph{Verification Reports} article type in the journal \emph{Cortex} \cite{chambers_verification_2020}.},
of computational results, i.e.,~checking that code generates the
output it claims to create, but not a validation, i.e.,~checking that
the code implements the right algorithm to solve the specific research
problem.  Nevertheless, simply attempting to reproduce an output may
highlight a submission's shortcomings in meeting a journal's
requirements (cf.~\cite{christian_journal_2020}) and may effectively
increase transparency, thereby improving practices
(cf.~\cite{nosek_scientific_2012}) even if the check does not go into
every detail.

\textbf{Step 4:} The CODECHECKER writes a certificate stating how the
code was run and includes a copy of outputs (e.g.,~data, figures, or
tables) that were independently generated.  The certificate may
include further recommendations on how to improve the material.  The
free text in the certificate can describe what was really checked,
because each workflow is unique.  Since no specific tool or platform
should be required, such that no authors are excluded, it would be
futile for the CODECHECKER to use automation or fixed checklists.

\textbf{Step 5:} The certificate and auxiliary files created
during the check, e.g.,~a specification of a computing environment, data 
subsets or helper scripts, and the original code and data get deposited in
an open archive unless restrictions (data size, license or 
sensitivity) apply.
Currently, the CODECHECKERs deposit the material on Zenodo themselves, but the PUBLISHER may complete this step after integrating CODECHECK into its review process.
A badge or other visual aid may be added to the deposit and the paper and
link to the certificate.
Although a badge simplifies the CODECHECK into a binary value and risks introducing confusion regarding the extent of the check, especially across disciplines and methods, a badge can provide recognition value and acknowledges the completed CODECHECK.
The badge and the actual check are incentives for undertaking the effort needed to provide a reproducible workflow.

\textbf{Step 6:} The PUBLISHER can, depending on the timing, provide the
certificate to peer-reviewers or editors or publish it
and link between  certificate, paper, and any repositories 
through metadata. Currently, the CODECHECKER creates these connections on
Zenodo. They appear as links with a relationship type on the Zenodo
landing page for a record in the right-hand sidebar, e.g., the 
``related identifiers'' and ``alternate identifiers'' 
of certificate \texttt{2020-025} \cite{cert-2020-025}.
The PUBLISHER also credits the CODECHECKER for their work by depositing
the activity in scholarly profiles, such as ORCID
(see peer review contributions in ORCID records,
\url{https://support.orcid.org/hc/en-us/articles/360006971333-Peer-Review}).
The PUBLISHER also ensures proper publication metadata, e.g.,~links from the 
certificate repository to the published paper or the original code repository.

@@

The journal \emph{ACM Transactions on Mathematical Software (TOMS)} 
recently established a ``Replicated Computational Results'' (RCR) review process
\cite{heroux_editorial_2015}, where ``replicable'' is the same as our
use of ``reproducible''.

Fifteen RCR Reports have been published so far (search on 
\url{https://search.crossref.org/} with the term
\texttt{"Replicated Computations Results (RCR) Report"} on 2020-12-10).
% 15: https://academic.microsoft.com/search?q=Replicated%20Computations%20Results%20%22(RCR)%20Report%22&f=&orderBy=0&skip=10&take=10
and the process is being extended extended to the ACM journal
\emph{Transactions on Modeling and Computer Simulation
  (TOMACS)} (cf. \url{https://dl.acm.org/journal/tomacs/author-guidelines}).
The TOMS RCR follows CODECHECK principles 1-4, although our work was
independently developed of theirs.  Here, we discuss variants of
CODECHECK, while TOMS RCR realises one particular workflow for
reproducibility reviews for one particular journal. The TOMS editorial
\cite{heroux_editorial_2015} shares similar concerns about selection
of reviewers, as we discussed above. Unlike existing CODECHECK
certificates, the RCR reports, which are similar to CODECHECK
certificates, undergo editorial review, but this could eventually
become part of the CODECHECK processes at journals.  The publication
of the RCR report is seen as a reward for the efforts of the
reproducing person, while the potential for this motive to be a
conflict of interest is acknowledged.  TOMS also recognises reviewer
activity in a partnership with Publons
(see \url{https://authors.acm.org/author-services/publons}).
It is unclear if the author of an RCR report receives both recognitions.
CODECHECK, however, specifically aims to give codecheckers
recognition as reviewers.  In our view, the reviewer role removes the
possible conflict of interest while keeping the public
acknowledgement.  Specific to the field of mathematics, the RCR is
also expected to apply a review of the software itself if the system
it runs on cannot be evaluated by an independent party.  The TOMS RCR
creators concur with the importance of communication, expect
collaboration between author and RCR reviewers, share the
considerations around reviewer selection, and also put trust in
reviewer judgement over numerical bit-wise perfection.  A key
difference is that for TOMS RCR, authors opt-in with an \emph{RCR
  Review Request} and the RCR reports are published in the TOMS
journal next to the actual papers.
%% SJE: think this could be tightened a bit, and some of it I don't
%% fully understand.

@@

Going beyond article types and a specific journal, the journal
\emph{ReScience C} (\url{https://rescience.github.io/}) publishes only
replications, also
requiring open code and replication by a third party. ReScience also
relies on free infrastructure (GitHub and Zenodo).

For research with very high stakes, where reproduction would be too weak and
post-publication replication possibly too late because of policy impact,
Benjamin-Chung et~al. \cite{benjamin-chung_internal_2020} propose
\emph{internal replication}.
A workflow that has undergone internal
replication would very likely be of high quality and relatively easy to check.
Similarly, internal CODECHECKs may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission.
Such internal checks are professionalised in local reproduction services,
such as CISER R-squared
(\url{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/})
or YARD (\url{https://isps.yale.edu/research/data/approach}),
or in communities such as Oxford's code review network (OxCRN,
\url{https://github.com/OxfordCodeReviewNet/forum}).

Gavis and Donoho \cite{gavish_universal_2011} propose a new discipline
and infrastructure for reproducible computational research with its
own tools and API. Their specific packaging format, provenance record,
and cryptographic \emph{Verifiable Result Identifier} would indeed
provide excellent reproducibility. However, the system is also complex
and since its creation in 2011 we are not aware of any publisher using
it; also, the system is not open source itself.  In comparison,
CODECHECK is less powerful but also much more flexible and less
dependent on specific tools or infrastructure. If data and code are
deposited properly, i.e.,~very unlikely to disappear, then the
certificate's DOI is practically close to the cryptographic
identifier.

@@

\textbf{Isn't CODECHECK what peer review should be doing already?}
On the surface, yes, but peer reviewers are overburdened enough and
asking them to do more work around peer review is not likely to
succeed.  Miyakawa described how when he as an editor simply requested
raw data from authors during submission, this led to almost all of
those papers in which data was requested to be withdrawn or rejected
after peer review \cite{miyakawa_no_2020}.  Such basic checks to show
that sufficient data supports the results requires effort from
editors, yet they only rely on the availability of data files and the
content of the paper.  These availability checks can be enhanced by
having more complex CODECHECKs request the code and then execute it.
This might fall within idealistic expectations of peer review, but is
rare.  Establishing a CODECHECK process is largely an acknowledgement
that peer reviewing practices have been unable to adapt to the
challenges of computational papers.  The concept of a CODECHECK, just
as the concepts of reproducible research and Open Science, may be
transitional by nature. If the activities described here as being part
of a CODECHECK become the norm for scientific reviews and
publications, then the initiative will have succeeded. However, the
rapidly changing technology used in research leads us to believe that
a separate role of codechecker and the expertise it brings will be
beneficial in the long term.

\textbf{Should CODECHECK requirements be more demanding?}
CODECHECK by design does not require authors to provide (and sustain)
an eternally functional workflow nor suggests a specific software
stack or practical approach.
Creating something
that anyone can reproduce has been called a fool's
errand (Douglas Blank on Twitter,
\url{https://twitter.com/DougBlank/status/1135904909663068165})
and we tend to agree.  However, the package of data, code, and
documentation collaboratively created by authors and codecheckers is a
snapshot of a working analysis that greatly increases the likelihood
of a successful reproduction and the possibility that a workflow can
be extended by third parties in the future, as long as they have
access to suitable resources and matching skill set.  Concrete
implementations of CODECHECK workflows, especially for specific
disciplines, may reify much more helpful guidelines for authors on how
to create reproducibility packages.  Our author-friendly ``low bar''
should not stay low forever, but cultural change takes time and the
encouragement and guidance that CODECHECK, as part of the widely
accepted peer review concept, can provide may eventually allow the bar
to be raised much higher, e.g.,~with executable research
compendia \cite{nust_opening_2017}, ``Whole Tales''
\cite{brinckman_computing_2018}, or continuous analysis
\cite{beaulieu-jones_reproducibility_2017-1}.  However, considering
that missing artefacts and lack of documentation have repeatedly been
identified as key barriers to reproducibility
(e.g.,~\cite{stagge_assessing_2019,nust_improving_2020}), we would not
underestimate the power of a simple check.  For example, ModelDB
curation policies require that only one figure need be manually reproduced
\cite{mcdougal_reproducibility_2016}, but that has not limited the
usefulness nor success of the platform.

@@

A codechecker does not conduct a \emph{code review}. Code reviews are
valuable to improve reproducibility and reusability, and their
proponents even believe they can improve the science
\cite{petre_code_2014}.  Code reviews, however, have quite different
structural challenges and require even more resources. That said, a
well-reviewed codebase is likely to be easier to codecheck, and the
awareness of high-quality code raised through CODECHECK may lead to
more support for code reviewing.  Initiatives and journals that
conduct software reviews independent of a specific publication or
workflow include ROpenSci (\url{https://ropensci.org/}),
PyOpenSci (\url{https://www.pyopensci.org/}), and
JOSS (\url{https://joss.theoj.org/}).  Furthermore, the
codechecker's task list is intentionally not overloaded with related
concerns, albeit potentially important ones, such as ensuring proper
citation of data and software or depositing data and software in
suitable repositories. Nevertheless, we expect codecheckers to often
recognise these issues and highlight them.

\textbf{How are failures during checks handled?}
We have not yet established a process for if a reproduction fails.  This
may simply reflect our biases in pre-selection of case studies.  In
the case that a journal adopts CODECHECK for all submissions, the open
question remains as what to do if a check fails, after exhausting
efforts between author and codechecker to reproduce the workflow.  A
negative comment in a CODECHECK certificate or a failed check does not
necessarily mean the paper or the science is bad (cf. discussion on
negative comments in \cite{everythinghertz123}).  We doubt that
publicly reporting failures (i.e.,~the code would not run) will
increase overall reproducibility, and it may prohibit authors from
sharing their best efforts, which is always more desirable than
nothing shared. Therefore, we recommend sharing the latest
draft of the certificate only with the authors, even if that
means that volunteer efforts may go unnoticed if no report is
published.  The most appropriate way forwards seems to be to give
private feedback for failures, public acknowledgment and
encouragement for successes, and recognise codecheckers as reviewers.
% eLife's new model (see https://osf.io/9cftx/) will publish reports eventually, e.g.,~after preprint has been accepted elsewhere
Rosenthal et~al. \cite{Rosenthal2016b} discuss such incentives for different actors around the
implementation of reproducibility. We see CODECHECK as one way for
organisations to invest in reproducibility by creating incentives
until reproducible computations become the norm.

@@

\textbf{Can't someone cheat?} Yes. We simply check that the code runs,
not that is correct or sound science. This ``mechanical'' test is
indeed a low bar.  By having the code and data openly deposited, third
parties can later examine the code, and we hope that knowing the code
will be open ensures that authors will not cheat.  It also allows
researchers, potentially with new methods, to look for errors.  This
is more effective than engaging in an arms race on building methods to
detect malicious intent now with closed datasets and code.  This is
analogous to storing blood samples of sport champions today to
possibly detect doping in the future with more sensitive methods
(cf. \cite{everythinghertz97}).  Another comparison that helped us
define the scope of a CODECHECK is that we think of the codechecker as
forensic photographer, capturing details so that an investigator may
later scrutinize them.

\textbf{Who's got time for more peer review?} Agree; codechecking
takes time that could otherwise be used for traditional peer review.
However, a CODECHECK is different from peer review.  First, the
\textbf{technical nature} of a CODECHECK sets clear expectations and
thereby time budget compared to conventional peer review.  For
example, authors are told what to provide and the codechecker can be
told when to stop.  Codecheckers can always directly ask the author
when clarification is required, thereby increasing
\textbf{efficiency}.  Second, the specific skill set of a codechecker
allows for \textbf{different groups} to participate in the review
process.  ECRs might be attracted to learn more about recent methods,
peer review, and reproducibility practices.  Research software experts
(Research Software Engineers,
RSE, see \url{https://en.wikipedia.org/wiki/Research_software_engineering})
who might not regularly be involved in writing or reviewing papers
might be interested in increasing their connection with scholarly
practices.  An extra codechecker may simplify the matchmaking an
editor does when identifying suitable reviewers for a submission,
as technical and topical expertise can be provided by different
people.  Third, recall that CODECHECKs should always be publicly
available, unlike peer review reports.  With code and workflows, the
codechecker's feedback may directly impact and improve the author's
work.  The public certificates and contributions provide \textbf{peer
  recognition} for the codechecker.  Fourth, we found that focusing on
workflow mechanics and interacting with the author makes reproductions
\textbf{educational}. It also is a different role and, as such, could
be a welcome option for researchers to give back their time to the
community.

@@

\textbf{Do workflows need to be codechecked multiple times?}  If a
paper is checked at the start of peer review, it might need
re-checking if the paper is modified during peer review.  This is
somewhat unavoidable, and has happened to us (e.g.,~certificate
\texttt{2020-012} \cite{cert-2020-012}). This can
also be desired though, if interactions between author, reviewer,
and codechecker led to improvements.  Checking the manuscript the
second time is likely to be much less work than the first time.

\textbf{What does it mean for a figure to be reproducible?}
Automatically detecting if a codechecker's results are ``the same'' as
an author's is more challenging than it might appear.  That is why we
do not require results to be \textit{identical} for a CODECHECK to pass
but simply that the code runs and generates output files that the
author claims. Stochastic simulations mean that often we cannot get
exactly the same results, and that even the same versions of libraries
can generate outputs that differ by operating system
\cite{Gronenschild2012-pp}.  While reproducibility practices can
mitigate some of these problems, e.g., by using a seed, the
flexibility of the human judgement is still needed, rather than
bitwise reproducibility.  The codechecker is free to comment on
visible differences in outputs in their report.

\textbf{Shouldn't the next step be more revolutionary?}  CODECHECK's
approach is to acknowledge shortcomings around computational
reproducibility and to iteratively improve the current system.  It
remains to be proven whether this approach is welcomed broadly and if
involving publishing stakeholders helps to further the cause.  We have
discussed more stringent rules at length, e.g. only considering fully
free and open source software, diamond Open Access journals, but we
eventually decided against them on the level of the principles.  For
the CODECHECK community
process, which is documented online at
\url{https://codecheck.org.uk/guide/community-process},
and the volunteer codechecker community, these requirements are
reconsidered.

We also have deliberated requiring modern technological solutions to
support reproducibility (cf.~\cite{konkol_publishing_2020}), but we
decided to focus on the human interface and the judgement of
experienced researchers and developers as a more sustainable and
flexible approach.  All types of research can adopt CODECHECK due to
its flexible design.  CODECHECK could include automated scoring
(e.g.,~\cite{menke_rigor_2020}), yet automation and metrics bear new
risks.  The focus of the CODECHECK principles on code execution allows
journals and publishers to innovate on financial  models and peer
review practices at their own pace.

@@

CODECHECK however harbours the same limitations as peer review in
general and is closely connected to larger disruptions and challenges
in scholarly communication
\cite{eglen_recent_2018,tennant_ten_2019,fyfe_mission_2019}, including
the tensions between commercial publishing and reviewers' often free
labour, and a global pandemic that has jumbled up scientific
publishing and exposed a broader general audience to science, even
preliminary results \cite{munafo_what_2020}.  Establishing CODECHECK
workflows must be seen as interconnected with much larger issues in
science, such as broken metrics or malpractice triggered by
publication pressure
\cite{piwowar_altmetrics:_2013,nosek_promoting_2015}.  We certainly do
not want the binary attribute of ``code works'' to become a factor in
bibliometric approaches for performance assessments.
% Mittermaier, Peer Review and Bibliometrics: http://hdl.handle.net/2128/22745

>>>>

\textbf{Step 1:} The author submits their manuscript along with the
code and data to the publisher.  The code and data need not be openly
available at this point.  However, in many cases the code and data may
be published on a code hosting platform, such as GitHub or
GitLab. Ideally, the author is expecting the CODECHECK and prepares
for it, e.g.,~by asking a colleague to attempt a reproduction, and
providing a set of instructions on how to re-run the workflow.

\textbf{Step 2:} The publisher finds a codechecker to check the
code. This is analogous to the publisher finding one or more
peer-reviewers to evaluate the paper, except we suggest that the
codechecker and the author talk directly to each other.

\textbf{Step 3:} The codechecker runs the code, based on instructions
provided by the author. They check if some or all of the results from
the paper can be reproduced. If there are any problems running the
code, the codechecker asks the author for help, updates, or further
documentation.  The burden to provide reproducible material lies with
the author.  The codechecker then tries to run the code again.  This
process iterates until either the codechecker is successful, or the
codechecker concludes the workflow is not reproducible.  As part of
this process, the codechecker could work entirely locally, relying on
their own computing resources, or in the cloud, e.g.,~using the open
MyBinder infrastructure \cite{jupyter_binder_2018} or alternatives,
some of which are more tailored to scientific publications while
others offer commercial options for, e.g.,~publishers
(cf. \cite{konkol_publishing_2020}).  A cloud-based infrastructure
allows for the codechecker and author to collaboratively improve the
code and enforces a complete definition of the computing environment;
but, unless secure infrastructure is provided, e.g.,~by the publisher,
this requires the code and data to be published openly online.  Note
that the task of the codechecker is to check the ``mechanics'' of the
workflow not to evaluate its correctness.  In the context of
mathematics, Stodden et~al. \cite{stodden_setting_2013} distinguish
between \emph{verification} and \emph{validation}; following their
definition, a CODECHECK ensures verification
%\footnote{Note this is a different use from that referred to as the \emph{Verification Reports} article type in the journal \emph{Cortex} \cite{chambers_verification_2020}.},
of computational results, i.e.,~checking that code generates the
output it claims to create, but not a validation, i.e.,~checking that
the code implements the right algorithm to solve the specific research
problem.  Nevertheless, simply attempting to reproduce an output may
highlight a submission's shortcomings in meeting a journal's
requirements (cf.~\cite{christian_journal_2020}) and may effectively
increase transparency, thereby improving practices
(cf.~\cite{nosek_scientific_2012}) even if the check does not go into
every detail.

\textbf{Step 4:} The codechecker writes a certificate stating how the
code was run and includes a copy of outputs (e.g.,~data, figures, or
tables) that were independently generated.  The certificate may
include further recommendations on how to improve the material.  The
free text in the certificate can describe what was really checked,
because each workflow is unique.  Since no specific tool or platform
should be required, such that no authors are excluded, it would be
futile for the codechecker to use automation or fixed checklists.

\textbf{Step 5:} The certificate and auxiliary files created during
the check, e.g.,~a specification of a computing environment, data
subsets or helper scripts, and the original code and data get
deposited in an open archive unless restrictions (data size, license
or sensitivity) apply.  Currently, the codecheckers deposit the
material on Zenodo themselves, but the publisher may complete this
step after integrating CODECHECK into its review process.  A badge or
other visual aid may be added to the deposit and the paper and link to
the certificate.  Although a badge simplifies the CODECHECK into a
binary value and risks introducing confusion regarding the extent of
the check, especially across disciplines and methods, a badge can
provide recognition value and acknowledges the completed CODECHECK.
The badge and the actual check are incentives for undertaking the
effort needed to provide a reproducible workflow.

\textbf{Step 6:} The publisher can, depending on the timing, provide
the certificate to peer-reviewers or editors or publish it and link
between certificate, paper, and any repositories through
metadata. Currently, the codechecker creates these connections on
Zenodo. They appear as links with a relationship type on the Zenodo
landing page for a record in the right-hand sidebar, e.g., the
``related identifiers'' and ``alternate identifiers'' of certificate
\texttt{2020-025} \cite{cert-2020-025}.  The publisher also credits
the codechecker for their work by depositing the activity in scholarly
profiles, such as ORCID (see peer review contributions in ORCID
records,
\url{https://support.orcid.org/hc/en-us/articles/360006971333-Peer-Review}).
The publisher also ensures proper publication metadata, e.g.,~links
from the certificate repository to the published paper or the original
code repository.

@@

The journal \emph{ACM Transactions on Mathematical Software (TOMS)}
recently established a ``Replicated Computational Results'' (RCR)
review process \cite{heroux_editorial_2015}, where ``replicable'' is
the same as our use of ``reproducible''.  Fifteen RCR Reports have
been published so far (search on \url{https://search.crossref.org/}
with the term \texttt{"Replicated Computations Results (RCR) Report"}
on 2020-12-10).
% 15: https://academic.microsoft.com/search?q=Replicated%20Computations%20Results%20%22(RCR)%20Report%22&f=&orderBy=0&skip=10&take=10
and the process is being extended extended to the ACM journal
\emph{Transactions on Modeling and Computer Simulation (TOMACS)}.
%% (cf. \url{https://dl.acm.org/journal/tomacs/author-guidelines}).
The TOMS RCR follows CODECHECK principles 1-4, although our work was
independently developed of theirs.  The TOMS editorial
\cite{heroux_editorial_2015} shares similar concerns about selection
of reviewers, as we discussed above. Unlike existing CODECHECK
certificates, the RCR reports undergo editorial review.  Publication
of the RCR report recognises the efforts of the reproducing person,
while the potential for this motive to be a conflict of interest is
acknowledged.  TOMS also recognises reviewer activity in a partnership
with Publons (see
\url{https://authors.acm.org/author-services/publons}).

This activity in the ACM journals can be seen as one possible workflow
within a CODECHECK system, and clearly shares much in spirit.
CODECHECK, however, specifically aims to give codecheckers recognition
as reviewers.  In our view, the reviewer role removes the possible
conflict of interest while keeping the public acknowledgement.
Specific to the field of mathematics, the RCR is also expected to
apply a review of the software itself if the system it runs on cannot
be evaluated by an independent party.  The TOMS RCR creators concur
with the importance of communication, expect collaboration between
author and RCR reviewers, share the considerations around reviewer
selection, and also put trust in reviewer judgement over numerical
bit-wise perfection.  A key difference is that for TOMS RCR, authors
opt-in with an \emph{RCR Review Request} and the RCR reports are
published in the TOMS journal next to the actual papers.

@@

Going beyond individual articles, the journal \emph{ReScience C}
(\url{https://rescience.github.io/}) publishes only replications, also
requiring open code and replication by a third party. ReScience also
relies on free infrastructure (GitHub and Zenodo).

For research with high stakes, where reproduction would be too weak and
post-publication replication possibly too late because of policy impact,
Benjamin-Chung et~al. \cite{benjamin-chung_internal_2020} propose
\emph{internal replication}.
A workflow that has undergone internal
replication would likely be of high quality and relatively easy to check.
Similarly, internal CODECHECKs may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission.
Such internal checks are professionalised in local reproduction services,
such as CISER R-squared
(\url{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/})
or YARD (\url{https://isps.yale.edu/research/data/approach}),
or in communities such as Oxford's code review network (OxCRN,
\url{https://github.com/OxfordCodeReviewNet/forum}).

Gavis and Donoho \cite{gavish_universal_2011} propose a new discipline
and infrastructure for reproducible computational research with its
own tools and API. Their specific packaging format, provenance record,
and cryptographic \emph{Verifiable Result Identifier} would indeed
provide excellent reproducibility. However, the system is also complex
and since its creation in 2011 we are not aware of any publisher using
it; also, the system is not open source.  In comparison,
CODECHECK is less powerful but also much more flexible and less
dependent on specific tools or infrastructure. If data and code are
deposited properly, i.e.,~very unlikely to disappear, then the
certificate's DOI is practically close to the cryptographic
identifier.

@@

\textbf{Isn't CODECHECK what peer review should be doing already?}  On
the surface, yes, but peer reviewers are overburdened enough and
asking them to do more work around peer review is not likely to
succeed.  When an editor (Tsuyoshi Miyakawa) requested raw data from
n=41 authors before reviewing, 21 authors withdrew their manuscripts;
19 of the 20 remaining articles were rejected after peer review
\cite{miyakawa_no_2020}.  Such basic checks require effort from
editors, yet they only rely on the availability of data files and the
content of the paper.  These availability checks can be enhanced by
having more complex CODECHECKs request the code and then execute it.
This might fall within idealistic expectations of peer review, but is
rare.  Establishing a CODECHECK process acknowledges that peer
reviewing practices have been unable to adapt to the challenges of
computational papers.  The concept of a CODECHECK, just as the
concepts of reproducible research and Open Science, may be
transitional by nature. If the activities described here as being part
of a CODECHECK are integrated into the publication process the
initiative will have succeeded.

\textbf{Should CODECHECK requirements be more demanding?}
CODECHECK by design does not require authors to provide (and sustain)
an eternally functional workflow nor suggests a specific software
stack or practical approach.
Creating something
that anyone can reproduce has been called a fool's
errand (\url{https://twitter.com/DougBlank/status/1135904909663068165})
and we tend to agree.  However, the package of data, code, and
documentation collaboratively created by authors and codecheckers is a
snapshot of a working analysis that greatly increases the likelihood
of a successful reproduction and the possibility that a workflow can
be extended by third parties in the future, if they have
access to suitable resources and matching skill set.  Concrete
implementations of CODECHECK workflows, especially for specific
disciplines, may reify much more helpful guidelines for authors on how
to create reproducibility packages.  Our author-friendly ``low bar''
should not stay low forever, but cultural change takes time and the
encouragement and guidance that CODECHECK, as part of the widely
accepted peer review concept, can provide may eventually allow the bar
to be raised much higher, e.g.,~with executable research
compendia \cite{nust_opening_2017}, ``Whole Tales''
\cite{brinckman_computing_2018}, or continuous analysis
\cite{beaulieu-jones_reproducibility_2017-1}.  However, considering
that missing artefacts and lack of documentation have repeatedly been
identified as key barriers to reproducibility
(e.g.,~\cite{stagge_assessing_2019,nust_improving_2020}), we would not
underestimate the power of a simple check.  For example, ModelDB
curation policies require that only one figure need be manually reproduced
\cite{mcdougal_reproducibility_2016}, but that has not limited the
usefulness nor success of the platform.

@@

A codechecker does not conduct a \emph{code review}. Code reviews are
valuable to improve reproducibility and reusability, and their
proponents even believe they can improve the research
\cite{petre_code_2014}.  Code reviews, however, have quite different
structural challenges and require even more resources. That said, a
well-reviewed codebase is likely to be easier to codecheck, and the
awareness of high-quality code raised through CODECHECK may lead to
more support for code reviewing.  Initiatives and journals that
conduct software reviews independent of a specific publication or
workflow include ROpenSci (\url{https://ropensci.org/}), PyOpenSci
(\url{https://www.pyopensci.org/}), and JOSS
(\url{https://joss.theoj.org/}).  Furthermore, the codechecker's task
list is intentionally not overloaded with related issues such as
ensuring proper citation of data and software or depositing material
in suitable repositories. Nevertheless, codecheckers are free to
highlight these issues.

\textbf{How are failures during checks handled?}

We do not yet have a process for denoting if a reproduction fails, as
our case-studies were all successful.  In the case that a journal
adopts CODECHECK for all submissions, the question remains as what to
do if a check fails, after exhausting efforts between author and
codechecker to reproduce the workflow.  A negative comment in a
CODECHECK certificate or a failed check does not necessarily mean the
paper or research is bad (cf. discussion on negative comments in
\cite{everythinghertz123}).  We doubt that publicly reporting failures
(i.e.,~the code would not run) will increase overall reproducibility,
and may prohibit authors from sharing their work, which is always more
desirable than nothing shared. Therefore, we recommend sharing interim
reproduction efforts only with the authors, even if that means that volunteer
efforts may go unnoticed if no certificate is published.  
% eLife's new model (see https://osf.io/9cftx/) will publish reports eventually, e.g.,~after preprint has been accepted elsewhere
Rosenthal et~al. \cite{Rosenthal2016b} discuss such incentives for
different actors around the implementation of reproducibility. We see
CODECHECK as one way for organisations to invest in reproducibility by
creating incentives until reproducible computations become the norm.

@@

\textbf{Can't someone cheat?} Yes. We simply check that the code runs,
not that is correct or sound science. This ``mechanical'' test is
indeed a low bar.  By having code and data openly deposited, third
parties can later examine the code, and we hope that knowing the code
will be open ensures that authors will not cheat.  It also allows
researchers, potentially with new methods, to look for errors.  This
is more effective than engaging in an arms race on building methods to
detect malicious intent now with closed datasets and code.  This is
analogous to storing blood samples of sport champions today to
possibly detect doping in the future with more sensitive methods
(cf. \cite{everythinghertz97}).  Another comparison that helped us
define the scope of a CODECHECK is that we think of the codechecker as
forensic photographer, capturing details so that an investigator may
later scrutinize them.

\textbf{Who's got time for more peer review?} Agree; codechecking
takes time that could otherwise be used for traditional peer review.
However, a CODECHECK is different from peer review.  First, the
\textbf{technical nature} of a CODECHECK sets clear expectations and
thereby time budget compared to conventional peer review.  For
example, authors are told what to provide and the codechecker can be
told when to stop.  Codecheckers can always directly ask the author
when clarification is required, thereby increasing
\textbf{efficiency}.  Second, the specific skill set of a codechecker
allows for \textbf{different groups} to participate in the review
process.  ECRs might be attracted to learn more about recent methods,
peer review, and reproducibility practices.  Research Software
Engineers (RSE) %% , see \url{https://en.wikipedia.org/wiki/Research_software_engineering})
who might not regularly be involved in writing or reviewing papers
might be interested in increasing their connection with scholarly
practices.  An extra codechecker may simplify the matchmaking an
editor does when identifying suitable reviewers for a submission,
as technical and topical expertise can be provided by different
people.  Third, recall that CODECHECKs should always be publicly
available, unlike peer review reports.  With code and workflows, the
codechecker's feedback may directly impact and improve the author's
work.  The public certificates and contributions provide \textbf{peer
  recognition} for the codechecker.  Fourth, we found that focusing on
workflow mechanics and interacting with the author makes reproductions
\textbf{educational}. It also is a different role and, as such, could
be a welcome option for researchers to give back their time to the
community.

@@

\textbf{Do workflows need to be codechecked multiple times?}  If a
paper is checked at the start of peer review, it might need
re-checking if the paper is modified during peer review.  This is
inevitable, and happened to us \cite{cert-2020-012}. This can
also be desired though, if interactions between author, reviewer,
and codechecker led to improvements.  Checking the manuscript the
second time is likely to be much less work than the first time.

\textbf{What does it mean for a figure to be reproducible?}
Automatically detecting if a codechecker's results are ``the same'' as
an author's is more challenging than it might appear.  That is why we
do not require results to be \textit{identical} for a CODECHECK to
pass but simply that the code runs and generates output files that the
author claims. Stochastic simulations mean that often we will get
different results, and even the same versions of libraries can
generate outputs that differ by operating system
\cite{Gronenschild2012-pp}.  While reproducibility practices can
mitigate some of these problems, e.g., by using a seed, the
flexibility of the human judgement is still needed, rather than
bitwise reproducibility.  The codechecker is free to comment on
visible differences in outputs in their report.

\textbf{Shouldn't the next step be more revolutionary?}  CODECHECK's
approach is to acknowledge shortcomings around computational
reproducibility and to iteratively improve the current system.  It
remains to be proven whether this approach is welcomed broadly and if
involving publishing stakeholders helps to further the cause.  We have
discussed more stringent rules at length, e.g. only considering fully
free and open source software, diamond Open Access journals, but we
eventually decided against them on the level of the principles.  For
the CODECHECK community
process, documented at
\url{https://codecheck.org.uk/guide/community-process},
and the volunteer codechecker community, these requirements can be 
reconsidered.

We have deliberated requiring modern technologies to support
reproducibility (cf.~\cite{konkol_publishing_2020}), 
focusing instead on the human interface and the judgement of experienced
researchers and developers as a more sustainable and flexible
approach.  All types of research can adopt CODECHECK due to its
flexible design.  CODECHECK could include automated scoring
(e.g.,~\cite{menke_rigor_2020}), yet automation and metrics bear new
risks.  The focus of the CODECHECK principles on code execution allows
journals and publishers to innovate on financial models and peer
review practices at their own pace.

@@

CODECHECK however harbours the same limitations as peer review in
general and is closely connected to larger disruptions and challenges
in scholarly communication
\cite{eglen_recent_2018,tennant_ten_2019,fyfe_mission_2019}, including
the tensions between commercial publishing and reviewers' often free
labour, and a global pandemic that has jumbled up academic
publishing and exposed a broader general audience to preprints
\cite{munafo_what_2020}.  Establishing CODECHECK
workflows must be seen as interconnected with much larger issues in
research, such as broken metrics or malpractice triggered by
publication pressure
\cite{piwowar_altmetrics:_2013,nosek_promoting_2015}.  We certainly do
not want the binary attribute of ``code works'' to become a factor in
bibliometric approaches for performance assessments.
% Mittermaier, Peer Review and Bibliometrics: http://hdl.handle.net/2128/22745
